Schramm-Loewner evolution in tricritical Ising model

### 2013-07-09 AffineLieAlgebras/Simons/paper.tex
Added kappa=5, s=3/5
Cardy values added

\begin{theorem}
  For tricritical Ising model on upper half plane there exists s-holomorphic observable $f$ given by the
  formula. It satisfies discrete boundary problem with boundary conditions. In the limit it
  converges to analytic function. Correlation function of something $F$ can be calculated as $F=f+if$.
\end{theorem}
\section{RSOS realization of the Ising and tricritical Ising model}
\label{sec:rsos-real-ising}

@@

  We are interested in the case $A_4$, so we have
$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.

@@

>>>>

\begin{theorem}
  For tricritical Ising model on upper half plane there exists s-holomorphic observable $f$ given by the
  formula. It satisfies discrete boundary problem with boundary conditions. In the limit it
  converges to analytic function. Correlation function of something
  $F$ can be calculated as $F=f+if$.

  $f$ is defined on dual lattice. 
  \begin{eqnarray}
    \label{eq:17}
    f=\sum_{C\in \mbox{conf}|\gamma:a\to z} W(C) e^{-i s \Theta}\\
    s=3/5\\
    \kappa=5
  \end{eqnarray}
\end{theorem}
\section{RSOS realization of the Ising and tricritical Ising model}
\label{sec:rsos-real-ising}

@@

  We are interested in the case $A_4$, so we have
$2\cos\lambda=\frac{1+\sqrt{5}}{2}$, $\lambda=\pi/5$, $\psi=\left[1,2\cos\lambda,2\cos\lambda,1\right]$.
$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.

@@

\begin{equation}
  \label{eq:12}
  \begin{array}{l}
    W\left(                                          
        \begin{array}{cc}
          2 & 1 \\
          1 & 2
        \end{array}
      \right)=
    W\left(
        \begin{array}{cc}
          3 & 4 \\
          4 & 3
        \end{array}
      \right)=   W\left(                                         
        \begin{array}{cc}
          1 & 2 \\
          2 & 1
        \end{array}
      \right)= \\
      W\left(                                                  
        \begin{array}{cc}
          4 & 3 \\
          3 & 4
        \end{array}
      \right)=\sqrt{\frac{2}{1+\sqrt{5}}}+\sqrt{\frac{1}{2}\left(1+\sqrt{5}\right)\\
    W\left(                                      
        \begin{array}{cc}
          2 & 3 \\
          1 & 2
        \end{array}
      \right)=
    W\left(                                         
        \begin{array}{cc}
          3 & 2 \\
          4 & 3
        \end{array}
      \right)=    W\left(                                         
        \begin{array}{cc}
          3 & 4 \\
          2 & 3
        \end{array}
      \right)=    W\left(                                         
        \begin{array}{cc}
          2 & 1 \\
          3 & 2
        \end{array}
      \right)=\\
    W\left(                                       
        \begin{array}{cc}
          3 & 2 \\
          2 & 1
        \end{array}
      \right)=
    W\left(                                                       
        \begin{array}{cc}
          1 & 2 \\
          2 & 3
        \end{array}
      \right)=    W\left(                                                      
        \begin{array}{cc}
          4 & 3 \\
          3 & 2
        \end{array}
      \right)=
    W\left(                                                        
        \begin{array}{cc}
          2 & 3 \\
          3 & 4
        \end{array}
      \right)=
\sqrt[4]{\frac{2}{1+\sqrt{5}}}\\
    W\left(
        \begin{array}{cc}
          3 & 2 \\
          2 & 3
        \end{array}
      \right)=    W\left(
        \begin{array}{cc}
          2 & 3 \\
          3 & 2
        \end{array}
      \right)=2
